---
title: "esercizi"
author: "Pertegato"
date: "4/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "esercizi22-78"
author: "Pertegato"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 22
# Create a data frame df from an arbitrary 5x5 matrix.
# Add to df a factor with levels "1" and "0".
```{r }
df <- data.frame(matrix(runif(25), 5, 5))
df <- data.frame(df, f=factor(rep(c(0,1), c(5,5))))


```

# Exercise 23
# Create a data frame df using three vectors and 1 factor (lengths > 5)
# Create a data frame df2 that is a subset of df binded with a 4x4 matrix
```{r }
df <- data.frame(v1=runif(10), v2=runif(10), v3=runif(10), f = factor(rep(c(0,1), c(5,5))))
df2 <- df[1:4,1:4]
df2
```

# Exercise 24
# Create a data frame df using a list containing 2 matrices with a 
# different number of columns  
```{r }
df <- data.frame(matrix(runif(25), 5, 5), matrix(runif(20),5,4))
df
```

# Exercise 25
# Create a data frame containing the data frame of the previous exercise plus a vector
# Extract one of the columns in three ways
```{r }
df1 <- data.frame(df,v1=runif(10))
df1["X1"]
df1[[1]]
df1[,1]
```

# Exercise 26
# Print the following attributes of the iris dataset:
# - class
# - dimensions
# - number of rows
# - number of columns
# - space occupied by the dataset
# - names attribute
```{r }
class(iris)
dim(iris)
nrow(iris)
ncol(iris)
object.size(iris)
names(iris)
```


# Exercise 27 - Summary - Objects in R
# Define a vector v with the following numbers: 27, 22, 23, 19, 21, 30 
# Print v
# Print the dimensions of v
# Print the length of v
# Print the class of v
# Assign to v the dimension (2,3)
# Print v
# Print the dimensions of v
# Print the class of v
# Assign to v the dimension NULL
# Define a factor s with the values: "M", "F", "M", "F", "F", "F"
# Print s
# Define a vector p with the strings: "Marco", "Monica", "Simone", "Giuliana", "Maria", "Marta"
# Print the class of p
# Use cbind to create a matrix M with columns p, v and s
# Print the class of each column of M
# Define a list l with the elements p, v and s
# Assign to l the names "Name", "Age" and "Gender"
# Print l
# Create a data frame using the list l
# Print the class of df
# Print df
# Print the class of each column of df
```{r }
v <- c(27,22,23,19,21,30)
v
dim(v)
length(v)
class(v)
v <- dim(c(2,3))
v
dim(v)
class(v)
v <- dim(NULL)
s <- factor(c(rep("M",1),rep("F",1),rep("M",1),rep("F",3)))
s
p <- c("Marco", "Monica", "Simone", "Giuliana", "Maria", "Marta")
class(p)
v <- c(27,22,23,19,21,30)
m <- cbind(p,v,s)
class(m[,1])
class(m[,2])
class(m[,3])
l <- list(p,v,s)
names(l) <- c("Name", "Age", "Gender")
l
df <- data.frame(l)
class(df)
df
class(df[[1]])
class(df[[2]])
class(df[[3]])

```

# Exercise 28
# Define a vector v with 20 numbers between 1 and 100
# Using a for loop, iterate over v and put in s the sum of the numbers greater than 50
```{r }
v <- runif(20,1,100)
s <- 0
for(i in v){
  if(i > 50){
    s = (s+i)
  }
}
s
```

# Exercise 29
# Define a 10x10 matrix m
# Iterate over m and set each element m[i,j] based on these rules:
# - if i != j then  m[i,j] = i*j
# - otherwise       m[i,j] = 1
```{r }
m <- matrix(runif(100),10,10)
m1 <- matrix(1,nrow(m), ncol(m))
for(i in seq_len(nrow(m))){
  for(j in seq_len(ncol(m))){
    if(i != j){
      m1[i,j] <- (m[i,j] = i*j)
    }else{
      m1[i,j] <- (m[i,j] = 1)
    }
  }
}
m1
```

# Exercise 30
# Define a 5x5 matrix m1 with numbers between 1 and 10 and a 5x2 matrix m2 with numbers from 1 to 10
# Using for loops calculate the matrix multiplication m1*m2. Put the result in m3
```{r }
m1 <- matrix(runif(1,10,25),5,5)
m2 <- matrix(runif(1,10,10),5,2)
m3 <- matrix(1,nrow(m1),ncol(m2))

for(i in nrow(m3)){
  for(j in ncol(m3)){
    m3[i,j] <- sum(m1[i,] * m2[,j])
  }
}
m3
```

# Exercise 31
# You're about to write your first function! Just like you would assign a value 
# to a variable with the assignment operator, you assign functions in the following
# way:
#
# function_name <- function(arg1, arg2){
#	# Manipulate arguments in some way
#	# Return a value
# }
#
# The "variable name" you assign will become the name of your function. arg1 and
# arg2 represent the arguments of your function. You can manipulate the arguments
# you specify within the function. After sourcing the function, you can use the 
# function by typing:
# 
# function_name(value1, value2)
#
# Below we will create a function called boring_function. This function takes
# the argument `x` as input, and returns the value of x without modifying it.
# Delete the pound sign in front of the x to make the function work! Be sure to 
# save this script and type submit() in the console after you make your changes.

boring_function <- function(x) {
  x
}

```{r }
boring_function <- function(x) {
  x
}
```

# Exercise 32
#Implement the function my_mean
# You're free to implement the function my_mean however you want, as long as it
# returns the average of all of the numbers in `my_vector`.
#
# Hint #1: sum() returns the sum of a vector.
# 	Ex: sum(c(1, 2, 3)) evaluates to 6
#
# Hint #2: length() returns the size of a vector.
# 	Ex: length(c(1, 2, 3)) evaluates to 3
#
# Hint #3: The mean of all the numbers in a vector is equal to the sum of all of
#		   the numbers in the vector divided by the size of the vector.
#
# Note for those of you feeling super clever: Please do not use the mean()
# function while writing this function!!!!!!

```{r }
myMean <- function(x) {
  sum(x) / length(x)
}
```

# Exercise 33
# You're going to write a function called "remainder." remainder() will take
# two arguments: "num" and "divisor" where "num" is divided by "divisor" and
# the remainder is returned. Imagine that you usually want to know the remainder
# when you divide by 2, so set the default value of "divisor" to 2. Please be
# sure that "num" is the first argument and "divisor" is the second argument.
#
# Hint #1: You can use the modulus operator %% to find the remainder.
#   Ex: 7 %% 4 evaluates to 3. 
#
# Remember to set appropriate default values!

remainder <- function(num, divisor) {
  num%%divisor
}

```{r }
remainder <- function(num, divisor) {
  num%%divisor
}
```

# Exercise 34
# You can pass functions as arguments to other functions just like you can pass
# data to functions. Let's say you define the following functions:
#
# add_two_numbers <- function(num1, num2){
#    num1 + num2
# }
#
# multiply_two_numbers <- function(num1, num2){
#	num1 * num2
# }
#
# some_function <- function(func){
#    func(2, 4)
# }
#
# As you can see we use the argument name "func" like a function inside of 
# "some_function()." By passing functions as arguments 
# some_function(add_two_numbers) willi evaluate to 6, while
# some_function(multiply_two_numbers) will evaluate to 8.
# 
# Finish the function definition below so that if a function is passed into the
# "func" argument and some data (like a vector) is passed into the dat argument
# the evaluate() function will return the result of dat being passed as an
# argument to func.
#
# Hints: This exercise is a little tricky so I'll provide a few example of how
# evaluate() should act:
#    1. evaluate(sum, c(2, 4, 6)) should evaluate to 12
#    2. evaluate(median, c(7, 40, 9)) should evaluate to 9
#    3. evaluate(floor, 11.1) should evaluate to 11


```{r }
evaluate <- function(func){
  func(c(2,4,6))
}
evaluate(sum)

evaluate1 <- function(func){
  func(c(7,40,9))
}
evaluate1(median)
evaluate <- function(func){
  func(11.1)
}
evaluate(floor)
```

# Exercise 35
# The syntax for creating new binary operators in R is unlike anything else in
# R, but it allows you to define a new syntax for your function. I would only
# recommend making your own binary operator if you plan on using it often!
#
# User-defined binary operators have the following syntax:
#      %[whatever]% 
# where [whatever] represents any valid variable name.
# 
# Let's say I wanted to define a binary operator that multiplied two numbers and
# then added one to the product. An implementation of that operator is below:
#
# "%mult_add_one%" <- function(left, right){ # Notice the quotation marks!
#   left * right + 1
# }
#
# I could then use this binary operator like `4 %mult_add_one% 5` which would
# evaluate to 21.
#
# Write your own binary operator below from absolute scratch! Your binary
# operator must be called %p% so that the expression:
#
#       "Good" %p% "job!"
#
# will evaluate to: "Good job!"

"%p%" <- function(p1,p2){ # Remember to add arguments!
 paste(p1,p2)
}

#You made your own binary operator! Let's test it out. Paste together the strings: 'I', 'love', 'R!'
#| using your new binary operator.

#> "I" %p% "love" %p% "R!"
#[1] "I love R!"
```{r }
"%p%" <- function(p1,p2){ # Remember to add arguments!
 paste(p1,p2)
}
"I" %p% "love" %p% "R!"

```
# Exercise 36
# Define a function even_count that takes in input a vector v and return the number of even elements of it.
```{r }
even_count <- function(v){
  sum(v[v%%2 == 0])
}

```

# Exercise 37
# Define a function m_create that takes 2 vectors v1, v2 and a variable n (by default = 10) that returns a matrix with n columns, 
# where each column is the concatenation of v1 and v2
```{r }
m_create <- function(v1,v2,n){
  matrix(rep(cbind(v1,v2),10),ncol = n)
}
```

# Exercise 38
# The ellipses can be used to pass on arguments to other functions that are
# used within the function you're writing. Usually a function that has the
# ellipses as an argument has the ellipses as the last argument. The usage of
# such a function would look like:
#
# ellipses_func(arg1, arg2 = TRUE, ...)
#
# In the above example arg1 has no default value, so a value must be provided
# for arg1. arg2 has a default value, and other arguments can come after arg2
# depending on how they're defined in the ellipses_func() documentation.
# Interestingly the usage for the paste function is as follows:
#
# paste (..., sep = " ", collapse = NULL)
#
# Notice that the ellipses is the first argument, and all other arguments after
# the ellipses have default values. This is a strict rule in R programming: all
# arguments after an ellipses must have default values. Take a look at the
# simon_says function below:
#
# simon_says <- function(...){
#   paste("Simon says:", ...)
# }
#
# The simon_says function works just like the paste function, except the
# begining of every string is prepended by the string "Simon says:"
#
# Telegrams used to be peppered with the words START and STOP in order to
# demarcate the beginning and end of sentences. Write a function below called 
# telegram that formats sentences for telegrams.
# For example the expression `telegram("Good", "morning")` should evaluate to:
# "START Good morning STOP"
```{r }
telegram <- function(...){
  paste("START",..., "STOP")
  
}

```

# Exercise 39
# Let's explore how to "unpack" arguments from an ellipses when you use the
# ellipses as an argument in a function. Below I have an example function that
# is supposed to add two explicitly named arguments called alpha and beta.
# 
# add_alpha_and_beta <- function(...){
#   # First we must capture the ellipsis inside of a list
#   # and then assign the list to a variable. Let's name this
#   # variable `args`.
#
#   args <- list(...)
#
#   # We're now going to assume that there are two named arguments within args
#   # with the names `alpha` and `beta.` We can extract named arguments from
#   # the args list by using the name of the argument and double brackets. The
#   # `args` variable is just a regular list after all!
#   
#   alpha <- args[["alpha"]]
#   beta  <- args[["beta"]]
#
#   # Then we return the sum of alpha and beta.
#
#   alpha + beta 
# }
#
# Have you ever played Mad Libs before? The function below will construct a
# sentence from parts of speech that you provide as arguments. We'll write most
# of the function, but you'll need to unpack the appropriate arguments from the
# ellipses.

mad_libs <- function(...){
  # Do your argument unpacking here!

  # Don't modify any code below this comment.
  # Notice the variables you'll need to create in order for the code below to
  # be functional!
  paste("News from", place, "today where", adjective, "students took to the streets in protest of the new", noun, "being installed on campus.")
}
```{r }
mad_libs <- function(...){
  args<-list(...)
  place <- args[["place"]]
   adjective <- args[["adjective"]]
   noun <- args[["noun"]]
   
  paste("News from", place, "today where", adjective, "students took to the streets in protest of the new", noun, "being installed on campus.") 
   
}
mad_libs(place='New Zealand', adjective='beautiful', noun='landscape')
```

# Exercise 40
# Define a function sum_vector that takes in input a undetermined number of vectors and returns a
# the sum of all elements. NA values on vectors must be ignored
# Use ellipsis function
```{r }
sum_vector <- function(...){
  args <- list(...)
  for(v in list){
    x <- x + sum(v , na.rm = TRUE)
  }
}
```

# Exercise 41
# Define a matrix_by_row function, with the same parameters of function "matrix()", 
# which fills the matrix by rows.
# Use ellipsis function
```{r }
matrix_by_row <- function(...){
  rbind(...)
}

```

# Exercise 42
# Dataset mtcars
# Show the number of cars by the number of cylinders (cyl)
# Show th average consumption (mpg) by the number of cylinders (cyl)
# Use only one instruction
```{r }
length(mtcars$cyl)
sum(mtcars$mpg) / length(mtcars$cyl)
```

# Exercise 43
# Visualize the first rows of the dataset iris
# Define a function iris_mean that takes as parameter a type of iris specie and returns
# a vector of the means of each column of that specie
# Use the function sapply
# Apply the previous function to all species
# Use for loop
```{r }
head(iris, n=1)
iris_mean <- function(type){
  
    sapply(iris[iris$Species == type, ][,1:4], mean)
}
iris_mean("setosa")
```

# Exercise 44
# Define a function "between" that takes as parameter: v, p and q. The function returns
# the number of elements of v that are between the values p and q (included).
# Define the following list: l <- list(c(23,232,112,2), c(23,33,33,22,32), c(12,34,65,67)).
# Apply the function between to l to obtain a vector of results
# Apply the function between to l to obtain a list of results
```{r }
between <- function(v,p,q){
  res <- c()
  t <- c(p,q)
  min <- min(t)
  max <- max(t)
  
  for(e in v){
    if(e >= min & e <= max){
      res <- c(res,e)
      
    }
  }
  return(res)
}
l <- list(c(23,232,112,2), c(23,33,33,22,32), c(12,34,65,67))
v1<- l[[2]]
between(v1,10,48)


```

# Exercise 45
# Create a data frame df with 4 columns. The first with a sample of 20 numbers between 1 and 100,
# the second with the value TRUE if the corresponding element is even (FALSE otherwise), the third with 
# the cube of the x elements. The names of the columns are: x, even, square and cube
# Write the first 10 rows of df (with the function write.table) in a file "powers1.csv". Each element of a row 
# must be separated with a ",". Hold the column names but not the row names.
# Write the last 10 rows of df (with the function write.csv) in a file "powers2.csv".
# Don't hold the row names.
# Merge the contents of files "powers1.csv" and "powers2.csv" in a file "powers3.csv".
# Use the function "read.table" or "read.csv"
```{r }
x <- sample(1:100,20)
even <- (x%%2 == 0)
df <- data.frame(x, even, square = x^2, cube = x^3)
names(df) <- c("x","even","square", "cube")
write.table(head(df,10), file = "powers1.csv", sep = ",", row.names = FALSE, col.names = TRUE)
write.csv(tail(df,10), file = "powers2.csv", row.names = FALSE)
write.csv(merge(head(df,10),tail(df,10)), file = "powers3.csv", row.names = FALSE)
read.table("powers1.csv", sep = ",")
read.csv("powers2.csv")
read.csv("powers3.csv")
```

# Exercise 46
# Use "read.table" to read data from the link "http://data.princeton.edu/wws509/datasets/effort.dat" with following:
# - "a", "b", "c" as columns names
# - number from 1 to 10 as row names
# - rows from 3 to 12
```{r }
read.table(file = "http://data.princeton.edu/wws509/datasets/effort.dat", col.names = c("a","b","c"), row.names =NULL ,nrows = 10, skip=2)
```

# Exercise 47
# Read the first 10 lines of the html page "http://www.r-project.org" in the variable x
# Print the class of x
# Put the elements of x with odd position in y
# Write the elements of y in a file "y_output.txt"
```{r }
x <- read.table(file ="http://www.r-project.org",sep = "\n", blank.lines.skip = TRUE)
x <- head(x,10)
class(x)
y <- x[x%%2 != 0]
s<-write.table(y, file = "y_output.txt", row.names = FALSE)
```


#Exercise 48
#Create two numeric vectors x and y of length 3 and 5 respectively. 
#What happens when you execute their product?
```{r }
x <- c(1,2,4)
y <- c(3,5,6,7,3)
x*y # recycling; the longer vector is not a multiple of the shorter one
```

#Exercise 49
#(a) Check if the current file is present in your current directory.
#(b) Then, choose another file from your current directory and get some informatin about it. 
#Do point (b) it in a single command.
```{r }
file.exists("C:/home/luca/Scrivania/Programming-laboratory-for-bioinformatics/esercizi 22-78.Rmd")

file.info("C:/home/luca/Scrivania/Programming-laboratory-for-bioinformatics/esercizi 22-78.Rmd")
```

#Exercise 50
#Write down the R code required to produce the following:
#(a) [1] 1 5 1 5 1 5 1 5 1 5 1 5 1 5 1 5 1 5 1 5 1 5 1 5 1 4 7 10 13 16 19
#(b) [1] 2 4 6 2 4 6 1 1 1 3 3 5 5 5 5
```{r }
c(rep(c(1,5),12), seq(1,19, by=3))
c(rep(c(2,4,6),2), rep(1,3), rep(3,2), rep(5,4))
```

#Exercise 51
#Calculate the sum of i^2 for i=3:177
```{r }
sum((3:177)^2)
```

#Exercise 52
#Use paste to obtain the following
#[1] "Ab-Bc-Cd-De-Ef-Fg-Gh-Hi-Ij-Jk-Kl-Lm-Mn-No-Op-Pq-Qr-Rs-St-Tu-Uv-Vw-Wx-Xy-Yz-Za"
#What is the difference between the parameters sep and collapse?
```{r }
paste(LETTERS, c(letters[-1],letters[1]), collapse = "-", sep = "")
# sep sta tra due elementi della stessa coppia e collapse sta tra ogni coppia
```

#Exercise 53
#Sample 50 values from x<-rep(NA,300) and y<-1:300 and put the result in a vector z
#Find the proportion of NAs in z in a single command.
```{r }
x <- rep(NA,300)
y <- 1:300
z <- c(sample(c(x,y),50))
sum(is.na(z)/length(z))
```

#Exercise 54
#Consider the vector z of the previous exercise. Modify it such that it contains only values greater than -50 
#but lower than 100(in a single command). NA values must be kept.
#What should be added in order to remove NA values?
```{r }
z <- z[z > -50 & z < 100]
z <- z[!is.na(z)]

```

#Exercise 55
#Create a vector x with named elements. Obtain the first element using three different ways. 
#Then modify x such that it does not contain the third element anymore. Do it by using names.
```{r }
x <- c(4,5,6)
names(x) <- c("A","B", "C")
x["A"]
x[[1]]
x[1]
x <- x[names(x) != 'C']
x
```

#Exercise 56
#Create a factor f containing the following levels: "BD Student" "MD Student". The repetitions should be 4 and 5 
#respectively.
#Then add a new level "PhD Student" for which the repetitions are still 0.
```{r }
f <- factor(rep(c("BD Student", "MD Student"), c(4,5)))
levels(f) <- c(levels(f), "PhD Student")
```

#Exercise 57
#Create a list l composed by the two following lists: 
l1<-list(name=c("Alberto","Antonio"),age=c(25,40),work=c("Student","Engineer"))
l2<-list(surname=c("Rossi","Bianchi"),nation=c("Italy","Malta"))
#(a)What happens if you use list to create l?
#(b)What happens when you type l$n and why? What should you type in order to obtain the nation component?
```{r }
l1<-list(name=c("Alberto","Antonio"),age=c(25,40),work=c("Student","Engineer"))
l2<-list(surname=c("Rossi","Bianchi"),nation=c("Italy","Malta"))
l3 <- list(l1,l2) #hai una lista che ha come elementi 2 liste
l$nation #we obtain null
l2[2]$nation
```

#Exercise 58
#Create a numeric matrix m 4x5.
#(a) Bind to m a numeric 4x2 matrix called n. Do both cbind and rbind work? If no, why?
#(b) Remove from the newly obtained m, the central column. Do this by exploiting the ncol function.
#(c) Multiply the new m matrix by n to obtain the row by columns product. Is it possible in this case?
#If not, how can we solve it?
```{r }
m <- matrix(runif(20),4,5)
n <- matrix(runif(8),4,2)
m1 <- cbind(m,n)
rbind(m,n) #doesn't work because number of columns of both matrices must correspond
m1 <- m1[, -ncol(m1)/2]
m1 %*% n #not possible
m1[c(1:4)] %*% cbind(n,n)
cbind(n,n) %*% m1
```

#Exercise 59
#(a) Create a matrix m 5x5 containing letters by using the sample function such that an element can appear more than once.
#Check the class of one of the elements of m.
#(b) Add a column of numbers. Check the class of one of the new elements of m. Is there something strange about it?
#(c) Which data structure could you use instead of the matrix? Create an appropriate data structure n
#containing the same elements of m.
#Then name your columns C1,...,C5 and your rows R1,...,R5 (do not use c())
#(d) Access to an element of n in 3 different ways. Does it remind you of another data structure?
```{r }
m <- matrix(sample(LETTERS,25, replace = TRUE),5,5)
class(m[1,1])
m <- cbind(m,c(1,1,1,1,1))
class(m[,6])
df <- data.frame(m)
colnames(df) <- c(paste("C", 1:6, sep=""))
rownames(df) <- c(paste("R", 1:5, sep=""))
df[[1]][1]
df$C1[1]
df[["C1"]][1]
```

#Exercise 60
#Create a 3D array a 3x3x4 containing numbers from 1:18.
#(a) Does recycling occur?
#(b) Select only the first row and all but the first column. Leave the third dimension intact. Do not subscribe a.
#(c) Copy a to a2.What happens if you set dim(a2) to NULL?
#(d) Transform a into a matrix.
```{r }
a <- array(1:18, c(3,3,4))
a1 <- a[,-1,]
a2 <- a
dim(a2) <- NULL
a3 <- cbind(a1[,,1], a1[,,2], a1[,,3], a1[,,4])


```

#Exercise 61
#Analyze the trees dataset.
#(a)Report its class,summary,structure,dimensions,size in bit,colnames and rownames.
#(b) What does R return if you type length(trees)?
#(c)Show the last 7 rows.
#(d) What is the frequency of the different values of Height? Round your result.
```{r }
View(trees)
class(trees)
summary(trees)
structure(trees)
dim(trees)
object.size(trees) 
colnames(trees)
rownames(trees)
#(b) What does R return if you type length(trees)?
length(trees) #returns 3
tail(trees, 7)
table(trees$Height) #for every value return how many elements correspond to that value.

```

#Exercise 62
#Consider the following matrix 
m<-matrix(sample(-20:20,50,replace=T),nrow=5)
#(a) Check if it contains any 0.
#(b) Check if it contains all positive integers
#(c) Which elements are greater than 15? How many are them?
```{r }
m<-matrix(sample(-20:20,50,replace=T),nrow=5)
any(m[,] == 0)
all(m[,] > 0)
m[which(m[,] > 15)] # which return a vector
length(m[which(m[,] > 15)])
```

#Exercise 63
#Replace each negative element of m with the corresponding positive one. Replace positive elements
#with their cube.Use control structures.
```{r }
for(i in nrow(m)){
  for(j in ncol(m)){
    if(m[i,j] < 0){
       m[i,j] = -(m[i,j])
    }else if (m[i,j] > 0){
        m[i,j]^3
    }else{
      
    }
  }
}
```

#Exercise 64
#Build a cycle where each time you sample a new integer between -20 and 30.
#Whenever you encounter an even number (not 0), print the square of the sum of all even numbers sampled until
#that moment.
#When 0 is sampled, exit from the cycle.
```{r }
s <- 0
f <- -1

while(f != 0){
  f <- sample(-20:30,1)
  if(f%%2 == 0 & f != 0){
    s <- (s + f)
    print(sum(s))^2
  }else if( f == 0){
    break;
  }else{
    
  }
}
```

#Exercise 65
#Define a function f that given a numeric vector, returns its maximum, minimum, median and mean value.
#Put these values in a vector, and return NULL if the input is not numeric. Test the function.
```{r }
f <- function(v){
  if(class(v) == "numeric"){
    return(c(min(v), max(v), mean(v), median(v)))
  }else{
    return(NULL)
  }
}

f(c(1,2,3,4))
```

#Exercise 66
#Define a function euclidean_dist that given a matrix return the euclidean distance between its rows Do not use
#the dist function. Test the function(compare it with dist).
```{r }
euclidean_dist <- function(ma){
  n = nrow(ma)
  edmat = matrix(0, nrow = n, ncol = n)
  for(i in (1:n)){
    for(j in (1:n)){
      edmat[i,j] = sqrt(sum(ma[i,],ma[,j])^2)
    }
  }
  edmat
}

```

#Exercise 67
#Define a function fact that given a number returns its factorial. Try not to use for loops
```{r }
fact <- function(x){
  factorial(x)
}

```

#Exercise 68
#Define a function that given a character vector, returns the frequency of the characters.
#HINT: Use the function strsplit to split the string.
#Test it with the following: AAAACCGGTCGACGGGACGG
```{r }
freq <- function(v){
  if(class(v) == "character"){
      table(strsplit(v,""))
  }
}
freq("AAAACCGGTCGACGGGACGG")
```

#Exercise 69
#Define a function with a variable number of input numeric arguments (minimum two) that does the following:
#(((a+b)*c)+d)*e and so on. Example: if the input is 4,5,6,7 what we want is ((4+5)*6)+7=61
#Test it using also length 1 vectors.
```{r }
my_function <- function(...){
  args <- list(...)
  first <- TRUE
  plus <- TRUE
  s <- 0
  if(length(args) < 2){
    print("Number of arguments not enough!")
    
  }else{
  for(v in 1:length(args))
    for(e in args[[v]]){
       if(first == TRUE){
        s <- e
        first <- FALSE
      }else if (plus == TRUE){
        s <- (s + e)
        plus <- FALSE
      }else{
        s <- (s * e)
        plus <- TRUE
      }
    }
    
  return(s)
  }
}
my_function(4,5,6,7)
```

#Exercise 70
#Consider the dataset esoph, which contains data from a case-control study of esophageal cancer in France.
#Analyze the dataset (how many features, how many samples, the size of the dataset).
#Provide a summary of it.
#Then
#(a) See how many people are there per each age group
#(b) Find the classes of each feature
#(c) Compute how many controls are in each age group 
#(d) Find how many unique vals exist per each feature. Do it in a single command
```{r }
nrow(esoph) #feature
nop <- sum(esoph$ncontrols, esoph$ncases) #samples 1175
dim(esoph)
by(esoph[,4:5], esoph$agegp, sum)
sapply(esoph,class)
tapply(esoph$ncontrols, esoph$agegp, sum)
sapply(sapply(esoph,unique), length)
```

#Exercise 71
#What is the difference between using vapply, sapply and lapply?
#When do sapply and lapply return the result in the same format?
```{r }
#apply() is the base function. It can be applied on matrix or 2 dim array only.
#lapply() can be applied on each element of a list. It also returns a list.
#sapply() is a wrapper function of lapply(). It stores the output in most simplified type.
# vapply() contains an extra argument FUN.VALUE where you can specify the type and length of the output that should be returned each time your applied function is called. 
```

#Exercise 72
#Consider the dataset state.x77, which contains statistics about the US. Consider also state.region,
#which indicates the location of each state.
#(a) Find the population for those states with an area greater than 100000 square miles(Single command).
#(b) Compute the mean of life Expectancy for each region(Northeast,South,North,Central,West)
```{r }
View(state.x77)
population <- state.x77[,1][which(state.area > 100000)]
tapply(state.x77[,4], state.region, mean)
```

#Exercise 73
#Make sure that that salary.txt is in your working directory.
#(a)Then execute the command below. What can you say about the first row of your file? How would you solve it?
sal<-read.table("salary.txt")
#(b) Select only those rows for which the degree is "doctorate" and put them into a new file called "doc_salary.txt".
#Remove the dg column. When writing the data to your file, specify new column names(sex,rank,year,year_since_deg,salary). 
#Use write.table.
#(c)Consider your doc_salary.txt file. Skip the first 5 lines and read only the first 10 among the remaining 
#ones. Use read.csv.
```{r }
file.exists("salary.txt")
sal<-read.table("salary.txt")
colnames(sal) <- sal[1,]
sal <- sal[-1,]
sal1 <- sal[which(sal$dg == 'doctorate'), ]
write.table(sal1, file = 'doc_salary.txt', quote = FALSE, col.names = TRUE)
d_sal <- read.csv('doc_salary.txt', sep = ' ', header = FALSE, col.names = c('sex','rank','year','year_since_deg','salary'))
```

#Exercise 74
#Use the command sample to generate a vector x of 20 random numbers between 1 and 20. Do it using the fewest number
#of parameters.
#What can you say about the frequency of the numbers in x?
#Now create a vector y of 20 random numbers between 1 and 20 but with the parameter replace to TRUE.
#What is the difference between y and x?
```{r }
x <- sample(1:20)
y <- sample(1:20, replace = TRUE)
#In y there are some values repeated
```

#Exercise 75
#Generate using two different R functions, 100 random and independent events which result can be either success
#or failure, knowing that in 85% of cases you will fail. Encode,if needed, 0 as failure and 1 as success.
#Then verify the proportion of successes and compare it with the expected probability. Is it different?
```{r }
flips <- sample(c(0,1), 100, replace = TRUE, prob = c(0.85,0.15))
flis2 <- rbinom(n = 100, size = 1, prob = 0.15) #100 obs of size 1 with probability of success of 0.15
sum(flips) / (length(flips)* 100)
sum(flis2)
#there is no difference
```

#Exercise 76
#(a)Generate a vector x of 100 random numbers extracted from a normal distribution with 0 mean and 1 sd.
#Using the function hist() plot the vector. Give a name to your plot.
#(b) Using the same command, generate a vector y of 1000 numbers, but with mean 10 and 30 sd.
#Plot the histogram and compare it with the one you've obtained before.
#(c) Compute the mean, standard deviation and variance of y and compare them with the theoretical values
#(look at the parameters of your command). Are they completely equal?
```{r }
x <- rnorm(100)
hist(x, main = "Random Plot")
y <- rnorm(1000,10,30)
hist(y)
mean(y)
sd(y)
var(y)
```

#Exercise 77
#Find the number of hours that are missing from December 25,2017. Use opportune data formats. 
#Find the weekday of December 25,2017 as well.
```{r }
x <- c(ISOdate(2020,11,09), ISOdate(2017,12,25))
difftime(x[1], x[2], units = 'hours')

weekdays(as.Date("2017-12-25"))
```

#Exercise 78
#Consider the setosa objects of the iris dataset.
#Make a plot with the sepal.width on the x axis, and the sepal.length on the y axis. 
#Color your points dark green, and change their shape to crosses (hint:use the help)
#Assign a title to your plot and your axis.
```{r }
setosa <- iris[iris$Species == 'setosa',]
plot(x = setosa$Sepal.Width, y = setosa$Sepal.Length, main = 'Setosa_Sepal', xlab = 'sepal_width', ylab = 'sepal_length', col = 'dark green', pch = 4)
```
