---
title: "Esercizi 1-21"
author: "Pertegato"
date: "9/10/2020"
output: html_document
---
# Exercise 1
# Create a directory "exercisesR". Inside the folder create another
# directory named "Es" and set it as working directory for R

```{r }
getwd()
setwd("~/Scrivania/Programming laboratory for bioinformatics/exerciseR/Es")
require("knitr")
opts_knit$set(root.dir = "~/crivania/Programming laboratory for bioinformatics/exerciseR/Es")
getwd()

```
# Exercise 2
# Open a help window for the mean function
```{r }
help(mean)

```
# Exercise 3
# Execute the operation sqrt(2*10 + 5), put the result in the variable x and print it to the screen.
```{r }
x<-sqrt(2*10 + 5)
x

```
# Exercise 4
# Define a vector v1 = (1,2,3,4,5), v2 = (23,13,1,33,2). Calculate the vector v3 = v1 + v2. Execute the 
# log10 of each element of v3 and put the result in v4. Print the square of each element of v4 
```{r }
v1<-c(1,2,3,4,5)
v2<-c(23,13,1,33,2)
v3=v1 + v2
v4<-log10(v3)
sqrt(v4)
```
# Exercise 5
# Print the sum of the squares of the first ten numbers using sequences. 
# Hint: the function sum(v) calculate the sum of the elements of the vector v.
```{r }
r<- 1:10
sum(sqrt(r))
```
# Exercise 6
# Print the sum of the first ten even numbers.
```{r }
(seq(2, 20, by=2))

```

# Exercise 7
# Create a vector v with ten numbers in the range (1,100). Print how many numbers are
# greater than 50.
# Hint: Use the function sum.
```{r }
v<- sample(seq(1, 100), 10)
v
my_na <-  v>50
my_na
sum(my_na)

```

# Exercise 8
# Define the following vector: v <- c(NA, NA, NA, NA, 1:100). Create a vector v2 from v with elements greater than 50
# but lower than 80. Exclude NA values.
```{r }
v <- c(NA, NA, NA, NA, 1:100)
v2<- v[v>50 & v<80 & !is.na(v)]
v2

```

# Exercise 9
# Define a vector v with elements from 1 to 20. Create a vector v2 with the odd elements of v.
# Assign to v2 a names vector with the letters of even position (from variable LETTERS). Print v2. 
# Use the negative indexing.
```{r }
v <- c(1:20)
v2 <- v[-c(seq(2, 22, by=2))]
names(v2) <- LETTERS[seq(1, by=2, length = length(v)/2)]
v2
```



# Exercise 10
# Build a factor of 25 elements (strings) formed by 3 different levels
```{r }
f <- factor(rep(c("A","C","G"),c(5,10,10)))
f
```

# Exercise 11
# Which data structures could be used to model a data set with a set of patients
# healthy and sick, subjected to 5 different types of clinical analysis?

data frame



# Exercise 12
# Create a list l with the following elements:
#   - a vector named seq with the first 10 numbers
#   - a vector named letters with the first 10 letters from LETTERS
#   - a vector named bool with some boolean values

# Print the length of l
# Print the elements of the vector "seq" using its name and its numerical index
# Print the second element of vector letters
# Add to l, as last element, the string "last"
```{r }
l<- list(seq=seq(10),letters=letters[seq( from = 1, to = 10 )],bool=logical(length = 7))
lenght<-length(l)
l[1]
l$seq
letters[2]
lenght

l <- c(l,"last")
l
```


# Exercise 13
# Given the list li <- list(m = matrix(rnorm(64), nrow = 8), s = c(rep("T", 3), rep("G", 5))) 
# - extract the second column of the matrix
# - the "G"s of the vector s
# Add to the list a vector of 10 random numbers.
# Access in 3 different ways to the second component of the list
# What is the difference between li[1] and li[[1]]?
# With the function diag, print the diagonal of the matrix of li
```{r }
li <- list(m = matrix(rnorm(64), nrow = 8), s = c(rep("T",3), rep("G",5)))
li[[1]][,2]
li[[2]][4:8]
li$vector = runif(10)
li$s
li[2]
li["s"]
#‘[[...]]’ is the operator used to select a single element, whereas ‘[...]’ is a general subscripting operator.
diag(li[[1]])
```

# Exercise 14
# Define a 5x5 matrix m formed by the numbers from 1 to 25. Assign names to columns and rows with the first 5 letters. 
# Create a new matrix m2, that is m without column 1 and 3 but a last column with all one named 'O'.
```{r }
m <- matrix((1:25), nrow = 5)
rownames(m) <- LETTERS[1:5]
colnames(m) <- LETTERS[1:5]
m2 <- m[,-c(1,3)]
m2 <- cbind(m2,1)

```

# Exercise 15
# Define a 5x5 matrix m with all one
# Define a 5x2 matrix m2 with the first 10 numbers.
# Put in m3 the result of matrix multiplication m*m2.
# Use %*% to multiply matrices
# Put m, m2 and m3 in a list l
# Print l

```{r }
m1 <- matrix(1, nrow = 5, ncol =5)
m2 <- matrix(1:10, nrow = 5, ncol = 2)
m3 <- m1 %*% m2
l <- list(m1,m2,m3)
l
```
# Exercise 16
# Create a 4x4 matrix m with the first 16 letters. Fill the matrix by rows.  
# Define a matrix m2 with all columns of m except the third
# Define a vector v with 4 arbitrary strings
# Create a matrix m3 which is the concatenation of m and v by columns
```{r }
m <- matrix(LETTERS[1:16], nrow = 4, ncol = 4, byrow = TRUE)
m2 <- m[,-3]
v <- c("ciao", "hi", "hello", "hola")
m3 <- cbind(m,v)
m3

```

# Exercise 17
# Build 2 matrices M and N with 5 columns. Build (if possible) with rbind a matrix with
# 5 columns and as rows, the rows of M and N. Is it possible build a matrix from M and N
# using cbind?

```{r }
M <- matrix(1, ncol = 5)
N <- matrix(2, ncol=5)
R <- rbind(M,N)
C <- cbind(M,N)
#yes, the result is a matrix with one row and ten columns

```

# Exercise 18
# Given 2 square matrices A and B (3x3) formed by random numbers, compute their element-wise
# product and their rows times columns product. Define a vector b with 3 elements and solve
# (function "solve") the linear system Ax = b.
```{r }
a <- matrix(runif(9),3,3)
b <- matrix(runif(9),3,3)
x1<-a*b
x2<- a %*% b
b1<-c(2,4,7)
j<-solve(a,b1)

```

# Exercise 19
# Build a 10x10 matrix composed by random numbers using at least two different ways.
# Use the functions matrix and array
```{r }
z<-matrix(runif(100), nrow = 10, ncol = 10)
z1<-array(runif(100), c(10,10))

```

# Exercise 20
# Build 2 matrices x (3x4) and y (5x3) of characters. Change the matrix x with a unique
# assignment in order to replace its first two columns with the last two rows of y
```{r }
x <- matrix("a", nrow = 3, ncol = 4)
y <- matrix("b", nrow = 5, ncol = 3)
x[,c(1,2)] <- t(y[c(4,5),])

```

# Exercise 21
# Build a 3x4x5 array formed by the first 60 positive natural numbers. Multiply a with
# an array with the same dimensions caracterized by random numbers. Is it possible
# multiply "a" with a vector with 60 numbers? If yes, what do you get?
# Modify "a" in order to obtain an array 4-D of dimensions 3x5x2x2. 
```{r }
a <- array(1:60, c(3,4,5))
d<-a * array(runif(60), c(3,4,5))
#Yes, we get a matrix of 3x4x5 composed by element-wise product of the two matrices
a <- array(a, c(3,5,2,2))
d
```