---
title: "Prova_ItinereR"
output: html_document
---


## ES 1
Which is the difference between sapply and lapply?

a) sapply returns a vector of results, while lapply returns a list of results
b) sapply returns a list of results, while lapply returns a vector of results
c) sapply takes a vector as input, while lapply takes a list as input
d) lapply can be used only on a data.frame objects, while sapply only on vectors
e) there is no difference
  

## ES 2

Which is the difference between array and matrix?

a) there is no difference
b) a matrix is a 2D vector, while an array is a 1D vector
c) a matrix is a 2D object, while an array is a multidimensional object
d) a matrix is a multidimensional object, while an array is a 1D object
e) arrays do not exist in R


## ES 3

What is the output of dim(v) where v is a vector of length 5?

a) 0
b) 1
c) 5
d) 1 5
e) NULL


## ES 4 

When would you use ellipsis in a function signature?

a) if the function does not take any argument
b) if you want to pass an indeterminate number of arguments to the function
c) if you want to pass only one indeterminate argument to the function
d) if you want to pass a maximum of three inderminate arguments to the function
e) if the function function accepts only lists as argument




## ES 5

Which is the aim of negative indexing in R (imagine to apply it on a vector v)?

a) to remove one element from the vector
b) to remove one or more element from the vector
c) to take the element in ith position starting from the end of the vector
d) to add one or more elements to a vector
e) to subset the vector starting form the end to its ith position




## ES 6
Consider iris dataset. Create a data.frame df containing only data related to setosa and virginica species. 
Do it in just one line of code.


```{r}

df <- iris[which(iris$Species == "virginica" | iris$Species == "setosa"),]
```

## ES 7 

Consider iris dataset, takes only the first two rows of data related to specie setosa and write them on an apporpriate file 

## ES 8

Transform the first string into the second one (Hint: use strsplit() function)

"HelloWorld"
"H_e_l_l_o_W_o_r_l_d"



## ES 9

Consider the "quakes" dataset which stores locations earthquakes of Fiji island since 1964.
Print the average earthquake wheigth by the Richter magnitude 
```{r}
#tapply
```

## ES 10


Write a function that takes an arbitrary number of numbers as strings eg: "1", "2", "3" and return their sum (Hint: use as.double())


## ES 11

define a binary operator that computes the sum of the square root of the means of two vectors. Use the following vectors

v1 <- c(25, 11, 34, 2, 17, 5)
v2 <- c(32, 16, 90, 45, 26 , 15, 3, 7)




## ES 12
Transform the following list into a data frame. If the columns have different lengths, fill them with NA.

```{r}
list(A = c(1:10), name= c("Luca", "Enza", "Mario", "Paola", "Martina"), B = c(rep("treated", 5), rep("untreated",5), drug = c(rep("aspirin",5))))

```

## ES 13  

Consider the data frame created in the preavious exercise, write a function to move the columns in even position in the rows at odd position and vice-versa. Change also rownames and colnames accordingly.


## ES 14

Create two matrices of dimensions 2x3 and 4x2, concatenate them by row, rename the columns using letters in even positions of the alphabet and rename the rows using the letters in the odd positions of the alphabet (which letters you want using LETTERS dataset).
Plot the first column values against the second column values.

## ES 15 

Given the two following data frames df1 and df2, take only the rows of them sharing the same rownames (Hint: use intersect()) and create a new data frame called df3 in which for each element you have the concatenation of the columns in df1 and df2. Create a binomial distribution using rbinom() using the data in df3 ( prob, the observation vector and the sum of size).
Finally print how many times each sample is sampled by rbinom(). 

```{r}
df1 <- data.frame(A = c("C",1, 0.1, 3), B= c("F",1, 0.05, 7), C = c("S",1, 0.2, 2), D =c("H", 1, 0.05, 4), E = c("Z", 1, 0.1, 5),
                  row.names = c("sample", "size", "prob", "observations"))

df2 <- data.frame(F= c(0.05, "Y", 1, 2.5, 3), G=c(0.1, "M", 1, 4.0, 4), H=c(0.1, "N", 1, 2.0, 6), I=c(0.05, "I", 1, 2.0, 5), 
                  L=c(0.2, "R", 1, 3.0, 8), row.names=c("prob","subject", "size", "measure", "observations"))



```
