---
title: "Prova_ItinereR"
output: html_document
---


## EX 1
Which is the difference between sapply and lapply?

a) sapply returns a vector of results, while lapply returns a list of results
b) sapply returns a list of results, while lapply returns a vector of results
c) sapply takes a vector as input, while lapply takes a list as input
d) lapply can be used only on a data.frame objects, while sapply only on vectors
e) there is no difference
  
## EX 2

Which is the difference between array and matrix?

a) there is no difference
b) a matrix is a 2D vector, while an array is a 1D vector
c) a matrix is a 2D object, while an array is a multidimensional object
d) a matrix is a multidimensional object, while an array is a 1D object
e) arrays do not exist in R

## EX 3

What is the output of dim(v) where v is a vector of length 5?

a) 0
b) 1
c) 5
d) 1 5
e) NULL

## EX 4 

When would you use ellipsis in a function signature?

a) if the function does not take any argument
b) if you want to pass an indeterminate number of arguments to the function
c) if you want to pass only one indeterminate argument to the function
d) if you want to pass a maximum of three inderminate arguments to the function
e) if the function function accepts only lists as argument

## EX 5

Which is the aim of negative indexing in R (imagine to apply it on a vector v)?

a) to remove one element from the vector
b) to remove one or more element from the vector
c) to take the element in ith position starting from the end of the vector
d) to add one or more elements to a vector
e) to subset the vector starting form the end to its ith position

## EX 6

Consider iris dataset. Create a data.frame df containing only data related to setosa and virginica species. 
Do it in just one line of code.
```{r}

df <- iris[which(iris$Species == "virginica" | iris$Species == "setosa"),]
```

## EX 7 

Consider the iris dataset. Subset iris dataset to obtain data related only to setosa specie and store the result in df. 
Then, take the first two rows of df and write them in an appropriate file. 

## EX 8

Consider the string "HelloWorld". Turn it in "H_e_l_l_o_W_o_r_l_d". (Hint: use strsplit() function)

## EX 9

Consider the quakes dataset, which stores earthquake locations of Fiji islands since 1964.
Print the average earthquake depth by Richter magnitude.
```{r}
#tapply
```

## EX 10

Write a function that takes an arbitrary number of numbers as strings (e.g. "1", "2", "3") and returns 
their sum. (Hint: use as.double())

## EX 11

Define a binary operator that computes the sum of the square root of the means of two vectors. Use the following vectors:

v1 <- c(25, 11, 34, 2, 17, 5)
v2 <- c(32, 16, 90, 45, 26 , 15, 3, 7)

## EX 12

Transform the given list into a data.frame object. If the columns of the resulting data.frame have different lengths, 
fill them with NA.
```{r}
list(A = c(1:10), name= c("Luca", "Enza", "Mario", "Paola", "Martina"), B = c(rep("treated", 5), rep("untreated",5), drug = c(rep("aspirin",5))))

```

## EX 13  

Consider the data.frame created during the preavious exercise. Write a function to exchange the columns in even position with
the rows in odd position and vice-versa. Change also rownames and colnames accordingly.

## EX 14

Create two matrices of dimensions 2x3 and 4x2. Fill them with random values. Then, concatenate them by row. Rename the columns 
using the letters (use R variable LETTERS) in even position and rename the rows using the letters in odd position.
Plot the values contained in the first column against those in the second column. (Hint: use runif(), LETTERS and plot())

## EX 15 

Consider the two data.frames df1 and df2. Extract the rows of df1 and df2 which share the same rownames. Then, create a new
data.frame called df3, containing the extracted rows concatenated by column. 
Use function rbinom() to create a binomial distribution, using data contained in df3 (prob, observations, size). 
Finally, print how many times each value has been sampled by rbinom().
(Hint: use intersect(), check the help for rbinom() and sum df3$size)

```{r}
df1 <- data.frame(A = c("C",1, 0.1, 3), B= c("F",1, 0.05, 7), C = c("S",1, 0.2, 2), D =c("H", 1, 0.05, 4), E = c("Z", 1, 0.1, 5),
                  row.names = c("sample", "size", "prob", "observations"))

df2 <- data.frame(F= c(0.05, "Y", 1, 2.5, 3), G=c(0.1, "M", 1, 4.0, 4), H=c(0.1, "N", 1, 2.0, 6), I=c(0.05, "I", 1, 2.0, 5), 
                  L=c(0.2, "R", 1, 3.0, 8), row.names=c("prob","subject", "size", "measure", "observations"))



```
