---
title: "Bash_Q&A_test.Rmd"
output: html_notebook
author: "Manuel Tognon, Simone Avesani"
---
  
## EX1
  
Assume that you are given a TSV file with 10 rows and 6 columns. The following command
```{bash}
cat "myFile.tsv"| head -n 5 | cut -f 6 | tail -n 4 
```
a) returns an error
b) prints the last 4 rows of the file
c) prints the first 4 rows of the file
d) prints the last 4 values of the sixth column
e) prints the second the third, the fourth and the fifth values of the sixth column
```{r}
e
```

## EX2
Assume that you are given a GFF file and assume that you want to extract the rows with data related to 
chromosome 1, for example.
Which bash command would you use?
  
a) grep
b) tar -xzf
c) cat
d) find
e) cut -f2 | grep 
```{r}
a
```

## EX3

Assume you are given a TSV file with 5 columns and 100 rows. Note that the first column contains the row 
indexes.
What the following command does, when applied to our file? 
```{bash}
sort -rk4
```
a) sort the rows in asceding order according to value in column 3
b) sort the rows in descending order according to value in column 3 
c) sort only the values in column 3 in descending order
d) print only the third column 
e) sort all the files containined in the directory containing the number 3 in the name in descending order
```{r}
b
```

## EX4

When writing values to a file, in Bash, which is the difference between `>` and `>>`?
  
a) there is not difference
b) > append the stdoutput at the end of the file, >> write on the std error
c) > append the stdoutput at the end of the file, >> redirect the std output to the file deleting the current 
   file content
d) > redirect the std output on the file deleting the current content, >> redirect the file content to the 
   standard input
e) > redirect the std output to the file deleting the current file content, >> append the stdoutput at the end
   of the file
```{r}
e
```

## EX5

Consider the TSV file `my_dataset.tsv`. 
Create a new file called `my_dataset_new.tsv` containing only the Sepal.Length, Sepal.Width and Species 
columns realted to "setosa" specie. Sort values in descending order by Sepal.Length. (Bonus: include the 
column names in the resulting TSV file).

```{bash}
filename="my_dataset.tsv"
cut -f 1,2,5 | awk = 'setosa' | sort -rk1 > $filename
#awk -f $filename c1=Sepal.Length c2=Sepal.Width c3=Type
head -n 1- $filename #or : awk 'NR==1 {print; exit}' $filename
mv $filename my_dataset.tsv

K=$(printf '\t')
k1="Sepal.Length"
k2="Sepal.Width"
k3="Species"
echo "$k1$K$k2$K$k3" > my_dataset_new.tsv
grep "setosa" my_dataset.tsv | cut -f 1,2,5 | sort -rk1 >> my_dataset_new.tsv

head -n 1 my_dataset.tsv | cut -f 1,2,5 > my_dataset_new.tsv
grep "setosa" my_dataset.tsv | cut -1,2,5 | sort -rk1 >> my_dataset_new.tsv
```

## EX6

Create a new directory called `my_dir` and rename it as `my_dir2`. Create inside `my_dir2` a TXT file called 
`my_file.txt`. Write in `my_file.txt` a numeric sequence from 1 to 10.
```{bash}
mkdir my_dir
mv my_dir my_dir2
touch my_file.txt
seq= seq 1 10
echo "$seq"> my_dir2/my_file.txt

```

## EX7

Consider the GFF file `grafimo_out.gff`. Create a file named `grafimo_out_fwd.gff` containing only data 
related to forward DNA strand ('+') and a file named `grafimo_out_rev.gff`, containing only data related to
the reverse strand ('-'). Include the GFF header in the output files. (Hint: the strand information are in 
the 7th column and type `man awk` on terminal).
```{bash}
filename="grafimo_out.gff"
filenamea="grafimo_out_fwd.gff"
filenameb="grafimo_out_rev.gff"
head -n 1 $filename > $filenamea
head -n 1 $filename > $filenameb
cat $filename | awk '/\+/ {print}' >> $filenamea
cat $filename | awk '/\t-\t/ {print}' >> $filenameb #\t =between columns

filename="grafimo_out.gff"
filenamea="grafimo_out_fwd.gff"
filenameb="grafimo_out_rev.gff"
head -n 1 $filename > $filenamea
head -n 1 $filename > $filenameb
cat $filename | sort -k7 | '/\+/ {print}' >> $filenamea
cat $filename | sort -k7 | awk '/\t-\t/ {print}' >> $filenameb 

```

## EX8 
Create a functions that, read a GFF file, prints the total number of features contained in the file, a 
function that prints the number of features belonging to the forward strand ('+') and one which prints those
belonging to reverse strand ('-'), a funtion that prints the number of features by chromosome and a funtion 
which computes the average score by chromosome. Consider `grafimo_out.gff` as input file. (Hint: the score is
in the 6th column, while the strand is in the 7th column).

```{bash}
num_features grafimo_out.gff
num_frwrd_strnd grafimo_out.gff
num_rvrs_strnd grafimo_out.gff
num_chr grafimo_out.gff
score grafimo_out.gff

function num_features {
num_features = 'grep -v -P "^#" $1 | cut -f 3 | sort | uniq -c '
#not consider the first line  with #, select the rd column, sort and cosider uniq features
echo "Number of features: $num_features"
}

function num_frwrd_strnd {
num_frwrd = 'cat $1 | awk '/\+/ {print}' | cut -f 3 | sort | uniq -c'
echo "Number of features belonging to forward  strand ('+'): $num_frwrd"
}

function num_rvrs_strnd {
num_rvrs = 'cat $1 | awk '/\t-\t/ {print}' | cut -f 3 | sort | uniq -c'
echo "Number of features belonging to reverse strand ('-'): $num_rvrs"
}

function num_chr {
tmp='mktemp' 
tmp = 'cut -f 1 | sort | uniq -c'
while lines line 
  comparisons = 'grep "^$line" $1 | cut -f 3 | sort | uniq -c'
  #comparisons between chromosomes in the 3rd column, sorting and considering uniq features 
  echo $line
  echo comparisons
}

function score {
tmp='mktemp'
grep -v -P "^#" $1 | cut -f1 | sort | uniq > $tmp
echo "5-Score"
while read line # to scan the original file and consider chromosome by chromosome
  do  
    chr=$line
    tot4='grep "^$line" $1 | cut -f6 ' #grep  -v -P "^#" $1
    tot_score=0
    n=0
    for 1 in $tot4  #to scan the list of tot4
    do 
      tot_score='echo "(($tot_score * $n) + $1 ) / ($n + 1.0)" | bc -1'
      ((n=n+1))
    done
    echo "$chr $tot_score"
  done < $tmp
  rm $tmp
    
}
```

